%-------------------------
% Resume in Latex
% Author : Srilaxmi Nancharla
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemContent}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      % \textbf{#1} & #2 \\
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Srilaxmi Nancharla}} & Email : \href{mailto:srilaxminancharla23@gmail.com}{srilaxminancharla23@gmail.com}\\
  \href{https://www.linkedin.com/in/srilaxmi23//}{https://www.linkedin.com/in/srilaxmi23/} & Mobile : 9380704199 \\
   % \href{https://github.com/srilaxmi23670}{https://github.com/srilaxmi23670}
\end{tabular*}


% %
% %--------PROFESSIONAL SUMMARY------------
% \section{Professional Summary}
% {Software developer with 2 years expertise in agile methodologies and cross-functional teamwork to deliver high-quality solutions that meets business objectives efficiently.}
% % {Software developer with 2 years expertise in reactive stack Java development and Spring framework, designing, implementing, and maintaining scalable applications, leveraging modern software architecture principles. Skilled in agile methodologies and cross-functional teamwork to deliver high-quality solutions that meet business objectives efficiently.}



%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {NATIONAL INSTITUTE OF TECHNOLOGY, GOA}{Goa, India}
      {Bachelors of Technology in Electronics and Communications Engineering; GPA: 9.06}{Aug 2018 -- Apr 2022}
      \resumeSubHeadingListStart
      \resumeItemContent{Worked as Secretary for Team SPECTRA, an official ECE council.}
      \resumeItemListEnd
    \resumeSubheading
      {NARAYANA GROUP OF INSTITUTIONS, BACHUPALLY}{Hyderabad, India}
      {Higher Secondary Certificate in Maths, Physics, Chemistry; Marks: 985 (985/1000)}{Mar 2016 -- Mar 2018}
  \resumeSubHeadingListEnd



%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Turtlemint}{Pune, Inida}
      {Software Engineer}{Jul 2022 - Present}
      \resumeItemListStart

      \resumeItemContent{Developed and maintained a microservices-based architecture, ensuring high scalability and resilience through test-driven development for a reliable system.}
      \resumeItemContent{Revamped search functionality with advanced algorithms using MongoDB and Elasticsearch, achieving zero downtime and boosting suggestion accuracy by 20\%.}
      \resumeItemContent{Transformed service by configuring a versatile platform supporting diverse types, from standard schemas with precise constraints to insurer-specific uploads.}
      \resumeItemContent{Engineered a clean, maintainable codebase following SOLID principles; enhanced system reliability by 30\% and reduced post-release bugs by 50\%, leading to a significant decrease in support tickets.}
      \resumeItemContent{Implemented a flexible configuration framework enabling rapid schema adjustments and seamless integration of new data sources.}
      \resumeItemContent{Identified the requirements needed by product and vertical teams and provided support for their requirements and issues faced during integration.}

      \resumeItemListEnd

    \resumeSubSubheading
      {Tech Intern}{Jan 2022 - Jul 2022}
      \resumeItemListStart
      
        % \resumeItem{Research and Problem Solving}
          \resumeItemContent{Evaluated data mapping tools aligning project requirements by exploring client offerings.}
          \resumeItemContent{Demonstrated innovative and strategic thinking in the early stages of project development.}
          \resumeItemContent{Developed schema and drafted API contracts ensuring adherence to RESTful principles.}
        
      \resumeItemListEnd

    \resumeSubheading
      {NITI Aayog, Government of India}{Delhi, India}
      {Agriculture Vertical Intern}{Dec 2021 - Feb 2021}
      \resumeItemListStart
        % \resumeItem{Project Planning and Management}
          \resumeItemContent{Built 'NITIVet – Telemedicine for Livestock Health and Safety' website.}
          \resumeItemContent{Used for booking consultaion with a veterinary doctor with enhanced user interface.
        }
        \resumeItemContent{\href{https://drive.google.com/file/d/1es_FbVwxnpYvN2apLt0jYVZ2rLCrcefl/view?usp=sharing}{Received 'Excellent' performance rating from NITI Aayog, for exceptional contribution \faLink}}

    %   \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  % \resumeSubHeadingListStart
  \item{
     \textbf{Microwave Imaging}{: Gauss Seidel implementation for inverse problem in Microwave Imaging.} }
 \item{
     \textbf{Sudoku Game}  {: Designed a C++ GUI program for generating and playing Sudoku games, .}}
    % \resumeSubItem{
%        \resumeSubItem{Smart Traffic Control System}
%       {Implemented a Smart Traffic Control System using Arduino, featuring decoders,
% comparators, sensors, and modules for efficient traffic management.}
      
  \resumeSubHeadingListEnd


%
%-------- SKILLS------------
\section{Skills}
 \resumeItemListStart
    \item{
     \textbf{Technical Skills}{: Java, SpringBoot, Object-Oriented Programming (OOP), RESTful architecture, Data Structures and Algorithms (DSA), Low-Level Design (LLD), High-Level Design (HLD), Git, Github, Docker }
     }
    \item{
     \textbf{Databases}{: MongoDB, Redis, ElasticSearch, Kafka, OpenSearch }
    }
     % \item{
     % \textbf{Software Design and Architecture}{: DBMS, OOP, D}
     % }
    
 \resumeItemListEnd


%-----------ACHIEVEMENTS AND CERTIFICATIONS-----------------
\section{Achivements and Certifications}
  \resumeItemListStart
    \item {
     \href{https://coursera.org/share/04b5a9ed0ae3119d655fc2f711905c62}{ Completed Technical Support Fundamentals course on Coursera, demonstrating proficiency in troubleshooting techniques and IT support principles \faLink}
    
    }

    \item {
     \href{https://drive.google.com/file/d/1_2sQ7YmyKoDxdXu7vdadC9ebzHqom_Rr/view?usp=sharing}{Highly recommended by Samagra Foundation, Nashik, as a self-motivated, punctual, and creative intern with a strong professional behaviour \faLink}
    }
  \resumeItemListEnd


%-------------------------------------------
\end{document}
